A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-09-16 doc/large_strain.tex
add grant number for EPSRC

D.~Davydov acknowledges the financial support of the German Research Foundation (DFG), grant DA 1664/2-1.
D.~Davydov, D.~Arndt and J-P.~Pelteret are grateful to Jed Brown (CU Boulder) and Veselin Dobrev (Lawrence Livermore National Laboratory) for fruitful discussions on matrix-free operator evaluation approaches.
D.~Arndt and M.~Kronbichler were supported by the German Research Foundation (DFG) under the project ``High-order discontinuous
Galerkin for the exa-scale'' (\mbox{ExaDG}) within the priority program ``Software
for Exascale Computing'' (SPPEXA).
P.~Steinmann acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible, as well as funding by the EPSRC Strategic Support Package ``Engineering of Active Materials by Multiscale/Multiphysics Computational Mechanics''.

>>>>

D.~Davydov acknowledges the financial support of the German Research Foundation (DFG), grant DA 1664/2-1.
D.~Davydov, D.~Arndt and J-P.~Pelteret are grateful to Jed Brown (CU Boulder) and Veselin Dobrev (Lawrence Livermore National Laboratory) for fruitful discussions on matrix-free operator evaluation approaches.
D.~Arndt and M.~Kronbichler were supported by the German Research Foundation (DFG) under the project ``High-order discontinuous
Galerkin for the exa-scale'' (\mbox{ExaDG}) within the priority program ``Software
for Exascale Computing'' (SPPEXA).
P.~Steinmann acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible, as well as funding by the EPSRC Strategic Support Package ``Engineering of Active Materials by Multiscale/Multiphysics Computational Mechanics'' (EP/R008531/1).
